\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsthm, mathptmx,geometry}



\begin{document}
\begin{center}
	METRIC SPACES 2023-24\\
	ASSIGNMENT 1\\
	Due date: Monday of week 3 by 4pm.
\end{center}

\bigskip 

\begin{enumerate}
	\item Define $d_1: \mathbb{R}\times \mathbb{R} \to \mathbb{R}$ and $d_2: \mathbb{R}\times \mathbb{R} \to \mathbb{R}$  by 
	\[
	d_1(x,y)=(x-y)^2,
	\]
	and
	\[
	d_2(x,y)=\frac{|x-y|}{1+|x-y|}.
	\]
	Are $d_1$ and $d_2$ metrics? Prove your claims. 
	
	
	\item Let $(X,d)$ be a metric space, $c_1, c_2$ be points in $X$ and $r_1$, $r_2$ be positive real numbers. Prove that, if $B(c_1,r_1) \cap B(c_2,r_2) \not=\emptyset$ then $d(c_1, c_2) < r_1 + r_2$ (This says: if two open balls intersect, then the distance between their centers is smaller than the sum of their radii). Is the converse true? Give a proof or a counterexample.
\end{enumerate}

\section{Q1}
\begin{proof}

	\textbf{$d_1$ is not metric}, as triangular inequality does not hold.
	Let $a = 0, b = 1, c=2$, we have $d_1(a, c) = 4 > d_1(a, b) + d_1(b, c) = 2$.

	\textbf{$d_2$ is metric.} We are to demonstrate that it has the three required properties:\\
	1) $d_2(a,b) = 0 \iff |a-b| = 0 \iff a = b$. \\
	2) $d_2(a,b) = d_2(b, a)$ by definition of absolute value. \\
	3) To prove triangular inequality. Let us first consider function $f = \frac{x}{1+x}$. With $a\geq b>0$, we have $\frac{1}{1+a} \leq  \frac{1}{1+b} \implies \frac{-1}{1+a} \geq  \frac{-1}{1+b} \implies \frac{a}{1+a} = 1-\frac{1}{1+a} \geq  1 - \frac{1}{1+b} = \frac{b}{1+b}$, i.e, $a\geq b \implies f(a) \geq  f(b)$.

	By triangular inequality of absolute value, we know $|a-b| \leq  |a-c| + |b-c| \implies f(|a-b|) \leq  f(|a-c| + |b-c|) \implies \frac{|a-b|}{1+|a-b|} \leq  \frac{|a-c| + |b-c|}{1+|a-c| + |b-c|} = \frac{|a-c|}{1+|a-c|+|b-c|} + \frac{|b-c|}{1+|a-c|+|b-c|}  \leq \frac{|a-c|}{1+|a-c|} + \frac{|b-c|}{1+|b-c|}$, that is, $d_2(a,b) \leq d_2(a,c) + d_2(b,c)$ as desired.

\end{proof}

\section{Q2}
If $B(c_1, r_1) \cap B(c_2, r_2) \neq \emptyset$, we are to prove that $r_1 + r_2 > d(c_1, c_2)$.
\begin{proof}
$a \in B(c_1, r_1) \cap B(c_2, r_2)$. By definition of open ball, $d(a, c_1) < r_1$ and $d(a, c_2) < r_2$. Apply triangular inequality we have $d(c_1, c_2) \leq d(c_1, a) + d(c_2, a) < r_1 + r_2$ as desired.

The converse is false for certain disconnected metric spaces.
Let the metric space $M = (0,1) \cup (2,3) \subset R$ equipped with standard metric. Let $c_1 = 1, r_1 = 1, c_2=2, r_2 = 1$. Clearly $|c_1 - c_2| < 2 = r_1 + r_2$ but there is nothing in the intersection of open ball.
\end{proof}
\end{document} 

