\documentclass[../note.tex]{subfiles}
\begin{document}

\section{Group: Definitions}

\begin{definition}[Group]
Group is a set $\mathbb{S}$ with an operation $\odot$ that fulfills the following four properties:
\begin{enumerate}
	\item Closure: $\forall a,b\in \mathbb{S}, a\odot b\in \mathbb{S}$.
	\item Associtivity: $\forall a, b, c \in \mathbb{S}, (a \odot b) \odot c = a \odot (b \odot c)$;
	\item Identity: $\exists e\in \mathbb{S}$ such that $a\odot e = e\odot a = a$ for all $a\in \mathbb{S}$;
	\item Inverse: $\forall a\in \mathbb{S}, \exists a^{-1}\in \mathbb{S}$ such that $a\odot a^{-1} = e$.
\end{enumerate}

\begin{remark}
	Operation, $\odot $, within the set $\bb{S}$ can be defined as a function: $\odot: \bb{S}\times \bb{S} \rightarrow \bb{S}$ with the notation $\odot (a,b)=a \odot b$.

	The definition of identity can not be simplified to $\exists e\in \mathbb{S}$ such that $a\odot e = a$ for all $a\in \mathbb{S}$. 
	Nothing has prevented us from arbitrating that for a certain set $\bb{S}$ and $a, b \in \bb{S}$, $a \odot b = a$ while $b \odot a\neq a$.

	In contrast, the definition of inverse needs not such emphasis. If a set $\bb{S}$ has the property of closure, associtivity, and identity, $\forall a\in \mathbb{S} \exists a^{-1}\in \mathbb{S}$ such that $a\odot a^{-1} = e$ would implies that $a^{-1}a = e$. Here is a quick proof.

	Let $b = a^{-1}$.
	$a b=e \implies a b b = b a b = b$ (multiply both sides of $e$ with $b$). We know $b$ itself has an inverse, denoted as $c$; thus $a b b c = b a b c = b c$, and by associtivity, $a b (b c) = a b b c = b a b c = ba(bc) \implies a b = b a$ = $e$.  
\end{remark}

\emph{Note On Notation}: When there is no confusion, the symbol $\odot$ is omitted. \label{notation:Omission_Of_Group_Operator}

\end{definition}
\begin{theorem}[Consequence of the Definition]
There are many non-obvious properties that directly follow the definition.
\begin{enumerate}
	\item $\forall a, p \in \bb{G},$ there exists a unique $b \in \bb{G}$ such that $a b = p$.
	\item $\forall a, p \in \bb{G},$ there exists a unique $b \in \bb{G}$ such that $b a = p$.
	\item The Equation Rule: $\forall a, b, c \in \bb{G},$ $a b = a c \implies b = c$.
	\item The uniqueness of Inverse: All element of group has one and only one inverse.
	\item General Associtivity: Parenthesis does not matter, as long as the order is the same: 
		$a b c d e f g \cdots  = (a ((b c) e (f g)\cdots) = \cdots$
	\item Order of Inverse: $(a b)^{-1}=b^{-1}a^{-1}$. Indeed $(a_1a_2a_3\dots a_n)^{-1} = a_n^{-1}a_{n-1}^{-1}\dots a_1^{-1}$.
\end{enumerate}
\end{theorem}

\begin{hypothesis}
	These are some of my hypothesis and thoughts.
	\begin{enumerate}
		\item different properties of odd finite groups and even finite groups
		\item If defining the reverto of the operation $\odot $ to be $\oslash $ as such: $a \odot b = a \oslash b^{-1}$. What are the sets such that it would be a group under both $\odot \& \oslash$?
		\item Can we have a set $\mathbb{S}$, such that under the operation $\odot $ we have $\forall a, b \in \mathbb{S}, a \odot b = b \odot  a$ but without associtivity? (Community without associtivity?)
	\end{enumerate}
\end{hypothesis}
\begin{definition}[Order of Group and element]
The order of the group $\mathbb{S}$ is $|\mathbb{S}|$ (How many elements it has). \\
The order of an element $s \in \mathbb{S}$ is the smallest integer $i$ such that $s^i = e.$ (If such $i$ exists)
\end{definition}

Here are some examples of groups. 
\begin{enumerate}
	\item $\mathbb{S}=\{e\}$
	\item $\mathbb{S} = \{e, a, b, c\}.$ With the following operation:
		1. All elements are their own inverse; 
		2. The group is abelian.
		2. $a \odot b = c, a \odot c = b, b \odot c = a$.
\end{enumerate}

\begin{definition}[Subgroup]
	\hypertarget{def:subgroup}{A} subgroup of a group $\mathbb{S}$ is a subset $\\mathbb{H}$ of $\mathbb{S}$ that is also a group under the same operation $\odot$. It is denoted as $ \mathbb{H}\leq \mathbb{S}$. If $\mathbb{H} \neq \mathbb{G}$, we call it a proper subgroup with notation $\mathbb{H}< \mathbb{S}$.
\end{definition}

\begin{theorem}[Test For Subgroup] 
	For group $\mathbb{S}$ and it subset$\mathbb{H} \subseteq \mathbb{S}$, $\mathbb{H}$ is a subgroup of $\mathbb{S}$ if and only if 
	\begin{enumerate}
		\item $\mathbb{H}$ is not empty 
		\item $\forall h,k \in \mathbb{H}, h\odot k^{-1} \in \mathbb{H}$.
	\end{enumerate}
\end{theorem}

\begin{theorem} [Immediate Consequence of Subgroup definition]
	Let $\bb{G}$ be a group and $\bb{S}\leq \bb{G}$. Let $g_i\in \bb{G}$ and $s_i \in \bb{S}$:
	\begin{enumerate}
		\item $g\notin \bb{S} \implies gs, sg \notin \bb{S}$; however, $g_1, g_2 \notin \bb{S}$ may not imply $g_1g_2 \notin \bb{S}$
	\end{enumerate}
\end{theorem}

Graphs can help us to construct/discover more examples of groups.

\begin{definition}[Graph]
	A graph is a finite set of vertices and edges connecting the vertices;
	or, with abstraction of set theory, a graph consists of two sets $\mathbb{V}$ and $\mathbb{E}$, where each element of $\mathbb{E}$ is an element of $\mathbb{V}\times \mathbb{V}.$
\end{definition}

\begin{definition}[Isomophisim]
	Isomophisim of a graph is a bjection of vertices that preseves all edges;
	or, $\exists$ bijective $ f:\mathbb{V}\to \mathbb{V}$, such that $\mathbb{E}'= \{(f(a),f(b))|a,b \in \mathbb{E}\}=\mathbb{E}$.
\end{definition}

\begin{definition}[Dihedral Group]
	The dihedral group of order $2n$ is the group of symmetries of a regular $n$-gon. It is the direct product of two copies of the cyclic group of order $n$.
\end{definition}

\begin{definition}[Cyclic Group]
Let $\mathbb{G}$ be a group and $g$ one of its element. Considering the set:
\[
	\mathbb{S} = \{\cdots g^{-2}, g^{-1}, e, g, g^1, g^2 \cdots\}  
\]
If $\mathbb{S}$ is finite, it is called a cyclic group. Most importantly, all sets of such form with inheritted operation must be a group.
\end{definition}

\begin{theorem}[Properties of Cyclic Group]
Here are some properties immediately follows the definition.
\begin{enumerate}
	\item All set in the form of the defintion of the cyclic group is a subgroup.
	\item \label{Cyclic_Inheritance}Any subgroup of a cyclic group is also cyclic.
\end{enumerate}	
\end{theorem}

\begin{proof}
	The first property would be obvious after the introduction of homomorphism \& isomophisim, as all cyclic group with $n$ elements are isomorphic to $\mathbb{Z}_n$.
	
	To prove the second property. Consider the cyclic group in the form of $e, g, g^2, \dots, g^n$. Let $\bb{S}$ be its subgroup, let $m$ be the smallest integer such that $g^m \in \bb{S}$ (such $m$ can always be found as $\bb{S}$ must not be empty and all cyclic groups are finite). We claim $m|n$, thus $\bb{S}$ is cyclic.

	If $m$ does not divides $n$, by eucilidean algorithm we can find $m'<m$ such that $am-bn=m'$, where $a,b$ are integers, which means $g^{m'}\in \bb{S}$, which contradicts our assumption.
\end{proof}

\begin{example}
An example of cyclic group is $\mathbb{Z}_n$. (Integer under modular $n$ addition);
\end{example}

\begin{proposition}[Number of Subgroup for $\mathbb{Z}_n$]
	The number of the subgroup of cyclic group $\mathbb{Z}_n$ is equal to the number of the divisor of $n$. (Proposed 27 Feb 2023)
\end{proposition}

\begin{definition}[Left Coset]

\end{definition}

\begin{theorem}[Lagrange Theorem]
Consider finite group $\mathbb{G}$ and its subgroup $\mathbb{S}$. $|\mathbb{S}|$ divides $|\mathbb{G}|.$	
\end{theorem}

\begin{proposition}
Lagrange theorem implies that:
for a group $\mathbb{G}$ and $g \in \mathbb{G}$:

\begin{enumerate}
	\item $\omega (g)$ divides $|\mathbb{G}|$; 
	\item $g^{|\mathbb{G}|}=e$;
\end{enumerate}
\end{proposition}

\begin{example}
	The followings demonstrate Lagrange Theorem.
	\begin{enumerate}
		\item $\mathbb{Z}_{10}$ under addition modula 10 and its subgroup $\mathbb{S} = \{0,2,4,6,10\}$. 
		$|\mathbb{Z}_{10}|=10, |\mathbb{S}|=5$.  
	\end{enumerate}
\end{example}
\begin{proof}[Proof of Lagrange Theorem]
	Let $\mathbb{G}=\{g_1, g_2, g_3, \cdots \}$ be a group and $\mathbb{S}= \{s_0, s_1, s_2, \cdots\}$(let $s_0=e$) be its subgroup. 
	If $\mathbb{S}=\mathbb{G},$ we are done. If not, sine detrimento universalitatis(without loss of generality), let  $g_i \notin \mathbb{S}$. 
	Consider the set: $\mathbb{D}_1=\{g_1s|s \in \mathbb{S}\}$. The set $\mathbb{D}_1$ has the following properties:
	\begin{enumerate}
		\item $g_1s \in \mathbb{D}_1 \rightarrow g_1s \in \mathbb{G}$ 
		\item $|\mathbb{D}_1| = |\mathbb{S}|$. 
		\item $(\forall d \in \mathbb{D}_1)$ the set $\mathbb{D}_1'=\{ds|s\in \mathbb{S}\}=\mathbb{D}_1$
		\item $g_1s \in \mathbb{D}_1 \rightarrow g_1s \notin \mathbb{S}.$ 
	\end{enumerate}
	Property I is true because $\mathbb{G}$ is a group with the property closure.\\
	By claiming that $g_1s_i \neq g_1s_j$ for $i \neq j$ it is sufficently to show property II is true.
	
	To prove property III, we shall prove statement 1) $\mathbb{D}_1\subseteq \mathbb{D}_1'$ and 2) $\mathbb{D}_1'\subseteq \mathbb{D}_1$.
	To prove statement 1), consider $a\in \mathbb{D}_1$, $\exists s_1 \in \mathbb{S}$ such that $g_1s_1$. 
	Let $\mathbb{D}_1'$ be defined as $\mathbb{D}_1'=\{bs|s\in \mathbb{S}\}$. 
	and $b$ can be written in the form of $g_1s_2$. 
	Indeed $bs_2^{-1}s_1=a \rightarrow a\in \mathbb{D}_1' \rightarrow \mathbb{D}_1 \subseteq \mathbb{D}_1'.$ Statement 2) can be proved similarly.

	Property IV can be proved by contradiction. Assuming $\exists g_1s \in \mathbb{D}_1$ and $ g_1s \in \mathbb{S}.$ 
	We have $g_1ss^{-1} \in \mathbb{S}$ (by Inverse and Closure property of group) $\rightarrow g_1 \in \mathbb{S},$(by associtivity property of group) contradicting our assumption that $g \notin \mathbb{S}$.

	If $\mathbb{G}=\mathbb{S}\cup \mathbb{D}_1$, we are done, as $|\mathbb{G}| = 2|\mathbb{S}|$. 

	If $\exists g_2 \in \mathbb{G} \lor g_2 \notin \mathbb{S}, \mathbb{D}_1$. 
	Construct the set $\mathbb{D}_2=\{g_ws|s \in \mathbb{S}\}$. All elements in $\mathbb{D}_2$ have properties I, II of $\mathbb{D}_1$, and a stronger IV property: 
	$g_1s \in \mathbb{D}_2 \rightarrow g_1s \notin \mathbb{S}, \mathbb{D}_1.$.

	Thus by same reasoning, if $\mathbb{G}=\mathbb{S}\cup \mathbb{D}_1 \cup \mathbb{D}_2$, $|\mathbb{G}| = 3|\mathbb{S}|$.
	If not, we can constuct more disjoined sets $\mathbb{D}_3, \mathbb{D}_4, \cdots \mathbb{D}_n$ until the union of them and $\mathbb{S}$ forms $\mathbb{G}$. This can always be done as $\mathbb{G}$ is finite, and will have an order of $(n+1)\cdot |\mathbb{S}|. $
\end{proof}

\begin{proposition}[Some Application of Lagrange Theorem]\label{prop:Applic_lagrange}
	\ 
\begin{enumerate}
	\item \label{orderOfElement}For a group $\mathbb{G}$ with order $p$ and $k \in \mathbb{G}$ with order $q$; then $q$ divides $p$.
	\item \label{prime_cyclic} For a group $\mathbb{G}$ with prime order (i.e., $|\mathbb{G}|$ is prime), it must be a cyclic group.
\end{enumerate}
\end{proposition}

\begin{proof}
	\ref{prop:Applic_lagrange}.\ref{orderOfElement} implies \ref{prop:Applic_lagrange}.\ref{prime_cyclic}.
	To prove proposition \ref{prop:Applic_lagrange}.\ref{orderOfElement}, let $\mathbb{G}$ be a group and $\langle g\rangle$ be a cyclic group containing $g \in \mathbb{G}$, by langrange theorem $|\langle g\rangle|$ must divides $|\mathbb{G}|$.
\end{proof}

\end{document}
