\section{Question 2. Dold-Kan Correspondence}

\subsection{Nomalised Chain Complex}

Given a simplicial object, $A$ in the abelian category $\A$, we can construct a chain complex $N(A)$ called the \emph{normalised chain complex}.

\begin{definition}[Normalised Chain Complex \cite{weibel}]
	Let $A$ be a simplicial object in an abelian category $\A$. 
	The \emph{normalised chain complex} $N(A)$ is defined as the chain complex with
	\begin{itemize}
		\item $N_i(A) = 0$ for $i < 0$,
		\item $N_0(A) = A_0$.
		\item $N_n(A) = \bigcap_{i = 0}^{n - 1} \ker(\d_i: A_n \to A_{n - 1}) \subset A_n$,
		\item differential $d: N_n(A) \to N_{n - 1}(A)$ given by the restriction of $\d_n: A_n \to A_{n - 1}$ to $C_n(A)$.
	\end{itemize}
	$$
	\cdots \to N_n(A) \xrightarrow{\d_n} N_{n - 1}(A) \xrightarrow{\d_{n-1}} \cdots \xrightarrow{\d_2} N_1(A) \xrightarrow{\d_1} N_0(A) \to 0
	$$
\end{definition}

Note that the map $\d_n \d_{n-1} = \d_{n-1}\d_{n-1}$ by the simplicial identity \eqref{simp2}, so $dd N_n(A) = \d_{n-1} \d_{n-1} \bigcap_{i = 0}^{n-1} \ker(\d_i) = 0$, and $N(A)$ is a well defined chain complex.

Let $f: A \to B$ be a map of simplicial objects. 
Recall the map between simplical objects is a natural transformation, or, precisely, a sequence of maps $f_n: A_n \rightarrow B_n$ that makes the following diagram commute for all morphisms $\alpha: [m] \to [n]$ in $\D$:
\begin{equation}\label{natural-transformation-N}
\begin{tikzcd}
	A_n \arrow{r}{f_n} \arrow{d}{A(\alpha)} & B_n \arrow{d}{B(\alpha)} \\
	A_m \arrow{r}{f_m} & B_m
\end{tikzcd}
\end{equation}
Therefore we can define a map of chain complexes $N(f): N(A) \to N(B)$ by restricting $f_n: A_n \to B_n$ to $N_n(A)$ for each $n \geq 0$.
$N(f)$ can be visualised as the following diagram
\begin{equation}\label{chain-map-N}
	\begin{tikzcd}
		\cdots \arrow{r} & 
		N_n(A) \arrow{r}{\d_n} \arrow{d}{f_n} &
		\cdots \arrow{r}{\d_2} &
		N_1(A) \arrow{r}{\d_1} \arrow{d}{f_1} &
		N_0(A) \arrow{r} \arrow{d}{f_0} &
		0 \\
		\cdots \arrow{r} &
		N_n(B) \arrow{r}{\d_n} &
		\cdots \arrow{r}{\d_2} &
		N_1(B) \arrow{r}{\d_1} &
		N_0(B) \arrow{r} &
		0
	\end{tikzcd}
\end{equation}

Since each $\d_n$ is a restriction of the corresponding face map in the simplicial object, each smaller square in diagram \eqref{chain-map-N} is one copy of the the commutative diagram \eqref{natural-transformation-N}.
Therefore the digram \eqref{chain-map-N} commutes, and $N(f)$ is a well-defined map of chain complexes.

If $f = \text{id}$, then each $f_n = \text{id}_{A_n}$, and therefore $N(f) = \text{id}_{N(A)}$.
If $g: B \to C$ is another map of simplicial objects, then for each $n$, $(g f)_n = g_n f_n$, and therefore $N(gf)_n = g_n f_n|_{N_n(A)} = N(g)_n N(f)_n$. This proves that $N$ prerves identities and covariantly preserves composition of morphisms.
Therefore $N$ defines a covariant functor from the category of simplicial objects in $\A$ to the category of positive chain complexes in $\A$.
That is,
\begin{equation}
	N: [\D\op, \A] \to \Ch_{\geq 0}(\A).
\end{equation}

\subsection{Functor in Opposite Direction}


We may define another functor \cite{weibel} $K: \Ch_{\geq 0}(A) \rightarrow \CS\A$ in the opposite direction of $N$, where $\A$ is an abelian category.

Let $C$ be a positive chain complex in $\A$. 
We need to construct a simplicial object $K(C): \D\op \to \A$.
We follow the obesrvation \ref{sim-set-data}, and construct $K(C)$ by defining the objects $K(C)[n]$ for each $[n] \in \D$ together with appropriate maps between them corresponding to morphisms in $\D$.

Define $K(C)[n] := K_n(C)$ to be the finite direct sum 
\begin{equation}
	K_n(C) := \bigoplus_{p \leq n}\bigoplus_{\eta} C_p[\eta],
\end{equation}
Where $\eta$ runs over all surjective maps $\eta: [n] \to [p]$ in $\D$, and $C_p[\eta]$ is a copy of $C_p$ indexed by $\eta$, with $C_p$ is the $p$-th object in the chain complex $C$.
Here, the index by $\eta$ is a notational device to distinguish different copies of $C_p$ in the direct sum.

Concretely, 
$$
K_0(C) = C_0, \quad K_1(C) = C_0 \oplus C_1, \quad K_2(C) = C_0 \oplus C_1^{\oplus 2} \oplus C_2,  \cdots
$$

\begin{remark}\label{Number-n-p-sur}
Let $L(n, p)$ denote the number of surjective maps from $[n]$ to $[p]$ in $\D$.
We have the following results from purely combinatorics. 
	\begin{enumerate}
		\item $L(m, 0) = 1$ for all $m \geq 0$.
		\item $L(m, m) = 1$ for all $m \geq 0$.
		\item $L(n, m) = 0$ if $n < m$
		\item $L(n, m) = \binom{n+m+1}{m}$, which is the number of ways to put $n+1$ items into $m + 1$ bins allowing empty bins.
	\end{enumerate}
\end{remark}

Given a map $\alpha: [m] \rightarrow [n] \in \D$, we define the corresponding map $K(C)(\alpha): K_n(C) \to K_m(C)$ in the following way.
Since each $K_n(C)$ is a direct sum of copies of $C_p$ indexed by surjective maps $\eta: [n] \to [p]$, it suffices to define the map on each summand $C_p[\eta]$.

We have the following commutative diagram 
\begin{equation}\label{K-diagram}
	\begin{tikzcd}
		{[m]} \arrow{r}{\alpha} \arrow{d}{\eta'} & {[n]} \arrow{d}{\eta} \\
		{[q]} \arrow{r}{\epsilon} & {[p]}
	\end{tikzcd}
\end{equation}
Where $\epsilon \eta'$ is the unique epi-mono factorisation of $\eta \alpha$ as in theorem \ref{epi-mono-simplex} ($\eta$ is epic, $\epsilon$ is monic).
There are three cases to consider.
\begin{enumerate}
	\item If $q = p$, define $K(C)(\alpha)|_{C_p[\eta]} : C_p[\eta] \to C_q[\eta'] \subset K_m(C)$ to be the identity map $\text{id}_{C_p}$ between the two copies of $C_p$.
	\item If $q = p-1$ and the map $\epsilon$ is an inclusion. That is, $\epsilon = \epsilon_p$, the $p$-th face map in $\D$ ($\epsilon: [p-1] \rightarrow [p]$ that only misses $p$), we define $K(C)(\alpha)|_{C_p[\eta]} : C_p[\eta] \to C_{p-1}[\eta'] \subset K_m(C)$ to be the differential $d: C_p \to C_{p-1}$ in the chain complex $C$.
	\item In all other cases, define $K(C)(\alpha)|_{C_p[\eta]}$ to be the zero map
\end{enumerate}

Our first task is to show that this definition of $K(C)$ is well-defined simplicial object, i.e. a functor from $\D\op$ to $\A$.
There are two things to be checked. 
\begin{enumerate}
	\item Identities map in $\D$ are sent to identity maps in $\A$.
		Let us check its commutative diagram on each summand.
		\begin{equation}
	\begin{tikzcd}
		{[n]} \arrow{r}{\text{id}} \arrow{d}{\eta'} & {[n]} \arrow{d}{\eta} \\
		{[q]} \arrow{r}{\epsilon} & {[p]}
	\end{tikzcd}
	\cong
	\begin{tikzcd}
		{[n]} \arrow{r}{\text{id}} \arrow{d}{\eta} & {[n]} \arrow{d}{\eta} \\
		{[p]} \arrow{r}{\text{id}} & {[p]}
	\end{tikzcd}
	\end{equation}
	Since $\eta$ is surjective, and $\text{id}$ is injective, the unique epi-mono factorisation of $\eta \circ \text{id}$ is $\text{id} \circ \eta$.
	Soe by the first case of our definition, $K(C)(\text{id})|_{C_p[\eta]}$ is the identity map on each summand $C_p$, therefore $K(C)(\text{id}) = \text{id}_{K(C)}$.
	\item Composition of maps in $\D$ are sent to contravariant composition of maps in $\A$. 
		Again, let us check its commutative diagram on each summand. 
$$
\begin{tikzcd}
	{[m']}\arrow{r}{\alpha'} \arrow{d}{\eta''}& {[m]} \arrow{r}{\alpha} \arrow{d}{\eta'} & {[n]} \arrow{d}{\eta} \\
	{[q']}\arrow{r}{\epsilon'}  &{[q]} \arrow{r}{\epsilon} & {[p]}
\end{tikzcd}
$$
There are several cases to consider. Firstly, if both $\epsilon $ and $ \epsilon'$ and $\epsilon$ are identities, then $\epsilon \circ \epsilon'$ is identity and we have map on each summand is identity, so the composition holds.
If one of $\epsilon$ or $\epsilon'$ is identity while the other is inclusion, then their composition is inclusion, and corresponding map is the differential, so the composition holds.
In all other case we have the zero map, and the composition holds as well. (Recall composition of two differentials is zero in a chain complex.)
\end{enumerate}

This shows that for each positive chain complex $C$ in $\A$, our definition of $K(C)$ is indeed a simplicial object in $\A$.

To show $K$, is indeed a functor recall that a map of chain complexes $f: C \to D$ is a sequence of maps $f_n: C_n \to D_n$ that makes the following diagram commute
\begin{equation}
	\begin{tikzcd}
		\cdots \arrow{r} & 
		C_n \arrow{r}{\d_n} \arrow{d}{f_n} &
		C_{n-1} \arrow{r}{\d_{n-1}} \arrow{d}{f_{n-1}}&
		C_{n-2} \arrow{r}{\d_{n-2}} \arrow{d}{f_{n-2}} &
		\cdots\\
		\cdots \arrow{r} &
		D_n \arrow{r}{\d_n} &
		D_{n-1} \arrow{r}{\d_{n-1}} &
		D_{n-2} \arrow{r}{\d_{n-2}} &
		\cdots
	\end{tikzcd}
\end{equation}

Our defintion of the $n$-simplex $K_n(C)$ and $K_n{D}$ is 
\begin{equation*}
	K_n(C) := \bigoplus_{p \leq n}\bigoplus_{\eta} C_p[\eta], \quad
	K_n(D) := \bigoplus_{p \leq n}\bigoplus_{\eta} D_p[\eta].
\end{equation*}
We therefore define the induced map $K(f): K(C) \to K(D)$ is on each summand $C_p[\eta]$ as the map $f_p: C_p \to D_p$ between the two copies of $C_p$ and $D_p$ indexed by $\eta$.

To show that this is indeed a simplicial map we need to show that they satisfy the following naturality condition 

\begin{equation}\label{simplical-map-K}
	\begin{tikzcd}
		{K(C)_n} \arrow{r}{\alpha} \arrow{d}{(Kf)_n} & {K(C)_m} \arrow{d}{(Kf)_m} \\
		{K(D)_n} \arrow{r}{\alpha} & {K(D)_m}
	\end{tikzcd}
\end{equation}
where we have abused the notation, and use $\alpha: K(C)_n \rightarrow K(C)_m$ to denote that map induced by the order preserving map $\alpha: [m] \rightarrow [n]$ in $\D$

Let us first examine the upper right path $(Kf)_m \circ \alpha$. 
Again, we analyse its action on each summand $C_p[\eta]$ in $K(C)_n$.

By our definition, we need to consider the following commutative diagram
$$
\begin{tikzcd}
		{[m]} \arrow{r}{\alpha} \arrow{d}{\eta'} & {[n]} \arrow{d}{\eta} \\
		{[q]} \arrow{r}{\epsilon} & {[p]}
	\end{tikzcd}
$$
The map $\alpha|_{C_p[\epsilon]}$ depends on the nature of$\epsilon$.

Let us consider the lower left path on \ref{simplical-map-K}, that is $\alpha \circ (Kf)_n$. 
The key observation is that the square for $\alpha: K(D)_n \rightarrow K(D)_m$ is the same one!

So there are any three cases to consider, depending on the nature of $\epsilon$.
\begin{enumerate}
	\item If $\epsilon$ is identity, then both paths are the identity map on the summand $C_p[\eta]$ ($D_p[\eta]$), so the square of course commutes 
	\item If $\epsilon: [n-1] \rightarrow [n]$ is inclusion, then the induced $\alpha|_{C_p[\eta]}$ and $\alpha|_{D_p{\eta}}$ are both the differential maps in the chain complexes $C$ and $D$ respectively, they commute with the map $f$ as $f$ is a chain map.
	\item In all other cases the induced map is zero and is of course commutative.
\end{enumerate}

Moreover, the fact $K$ preserves identities and composition of morphisms covariantly is direct from our definitions

So we conclude that $K$ defines a covariant functor from the category of positive chain complexes in $\A$ to the category of simplicial objects in $\A$.

\subsection{Dold-Kan Correspondence}


The purpose of introducing the two functors $N$ and $K$ is to establish the Dold-Kan correspondence between simplicial objects in an abelian category $\A$ and positive chain complexes in $\A$.
This is stated in the following theorem. 

\begin{theorem}[Dold-Kan Correspondence \cite{weibel}]
	Let $\A$ be an abelian category. 
	The functor $N$ 
	\begin{equation}
		[\D\op, \A] \xrightarrow{N} \Ch_{\geq 0}(\A)
	\end{equation}
	define an equivalence of categories between the category of simplicial objects in $\A$ and the category of positive chain complexes in $\A$.
\end{theorem}

The key insight to prove this theorem is to show that the two functors $N$ and $K$ are inverse to each other. 
That is. $NK(C) \cong C$ and $KN(A) \cong A$.

Given a positive chain complex $C$, recall that 
$$
K_n(C) = \bigoplus_{p \leq n}\bigoplus_{\eta} C_p[\eta]
$$
where $\eta$ runs over all surjective maps $\eta: [n] \to [p]$ in $\D$. 
In particular, each $K_n(C)$ contains exactly one copy of $C_n$ as summand, which is indexed by the identity map $\text{id}_{[n]}: [n] \to [n]$.

Applying our previous definition, $NK(C)_n$, which is the $n$-th object in the normalised chain complex of the simplicial object $K(C)$, is given by
\begin{align*}
	NK(C)_n &= \bigcap_{i = 0}^{n - 1} \ker(\d_i: K_n(C) \to K_{n - 1}(C)) 
\end{align*}

By our definition, the face map $\d_i: K_n(C) \to K_{n - 1}(C)$ is induced by the face map $\epsilon^i: [n - 1] \to [n]$ in $\D$. 
By our definition of $K$, it acts on the unique $C_n = C_n[\text{id}_{[n]}]$ in the summand of $K_n$ according to the commutative diagram below.

\begin{equation*}
	\begin{tikzcd}
		{[n - 1]} \arrow{r}{\epsilon^i} \arrow{d}{\eta'} & {[n]} \arrow{d}{\text{id}} \\
		{[n - 1]} \arrow{r}{\epsilon} & {[n]}
	\end{tikzcd}
\end{equation*}

In this diagram, by definition $\text{id}\circ\epsilon^i$ will contains all elements in $[n]$ except $i$. 
Therefore, when $i \neq n$, the induced map on the summand $C_n$ is zero, and $C_n \subset NK(C)_n$.
Moreover, when $i = n$, the induced map on the summand $C_n$ is the differential $d: C_n \to C_{n - 1}$ in the chain complex $C$.

In similar fashion we can show for any other summand $C_p[\eta]$ in $K_n(C)$ the induced map will be zero.
Therefore each $NK(C)_n \cong C_n$ and the connecting differential maps are the same differential maps of $C$.
Therefore $NK(C) \cong C$.

To show that $KN(A) \cong A$ for a simplicial object $A$ is more involved.
Firstly, define a natural simplicial map $\psi_A: KN(A) \rightarrow A$ as follows.

For each $\eta: [n] \rightarrow  [p]$, the corresponding summand $KN(A)_n$ is $N_p(A)$, is a subobject of $A_p$.
We can define restriction of $\psi_A$ to this summand to be $N_p(A) \subset A_p \xrightarrow{\eta} A_n$, where the map $\eta: A_p \rightarrow A_n$ is the induced map by the morphism $\eta$ in $\D$.

For a morphism $\alpha: [m] \to [n]$ in $\D$, we have the following commutative diagram; therefore $\psi$ is indeed a natural transformation.
\begin{equation*}
	\begin{tikzcd}
		KN_n(A) \supset \arrow{d}{\alpha} & N_p(A) \arrow{d}{\epsilon} & \subset A_p\arrow{r}{\eta} & A_n  \arrow{d}{\alpha}\\
		KN_m(A) \supset & N_q(A) & \subset A_q \arrow{r}{\eta'} & A_m
	\end{tikzcd}
\end{equation*}

Notice that $N \psi_A: NKN(A) \rightarrow N(A)$ is an isomorphism by the previous part of the proof $NK(NA) \cong NA$. 

We can use the following lemma, which is lemma 8.4.5 in \cite{weibel} to conclude that $\psi_A$ is an isomorphism, therefore $KN(A) \cong A$.

\begin{lemma}
	Let $f: A \to B$ be a map of simplicial objects in an abelian category $\A$. 
	If the induced map of normalised chain complexes $N(f): N(A) \to N(B)$ is an isomorphism, then $f$ is an isomorphism.
\end{lemma}

\section{Q3. Simplicial Homotopy}

Simplicial homotopy between two simplicial maps is defined as follows.

\begin{definition}[Simplicial Homotopy \cite{weibel}]\label{simplicial-homotopy}
Given two maps of simplicial objects $f, g: A \to B$, where $A$ and $B$ are objects in abelian category $\A$, a \emph{simplicial homotopy} from $f$ to $g$ is a collection of $n+1$ maps $h_i: A_n \to B_{n + 1}$ for each $n \geq 0$ such that the following identities hold for all $n \geq 0$ and $0 \leq i \leq n + 1$:
\begin{align}
	\d_0 h_0 &= f  \label{homotopy1}\\ 
	\d_{n + 1} h_n &= g  \label{homotopy2}\\
	\d_i h_j &= \begin{cases}
		h_{j-1} \d_i & i < j \\
		\d_{i} h_{i - 1} & i = j \neq 0 \\
		h_j \d_{i - 1} & i > j + 1
	\end{cases}  \label{homotopy3}\\
	\sigma_i h_j &= \begin{cases}
		h_{j+1} \sigma_i & i \leq j \\
		h_{j} \sigma_{i - 1} & i >j
	\end{cases} \label{homotopy4}
	\end{align}
\end{definition}

It can be shown \cite{weibel} that simplicial homotopy in abelian category has is one-to-one correspondent to the following commutative diagram. 
\begin{figure} 
	\centering
\begin{tikzpicture}[>=Stealth]
  % Nodes
	\node (A) {$A \times \Delta[1]$};
	\node[left=of A] (D) {$A \times \Delta[0]$};
	\node[right=of A] (B) {$A \times \Delta[0]$};
	\node[below=of A] (C) {$B$};

  % Arrows (legs of the right triangle)
	\draw[<-] (A) -- node[above] {$\text{id} \times \epsilon_1$} (B);
	\draw[->] (D) -- node[above] {$\text{id} \times \epsilon_0$} (A);
	\draw[<-] (C) -- node[below right] {$g$} (B);
	\draw[->] (D) -- node[below left] {$f$} (C);
    \draw[->] (A) -- node[left] {$\gamma$} (C);
\end{tikzpicture}
\caption{Simplicial Homotopy Diagram}
\label{simplicial-homotopy-diagram}
\end{figure}

Where $\text{id} \times \epsilon: A \times \Delta[0]$ is defined as $(a, \alpha) \mapsto (a, \epsilon \circ \alpha)$, for $\alpha: [n] \to [0]$ in $\Delta[0]$.

Notice that $\Delta[1]_n = \H([n], [1])$ has exactly $n + 2$ elements, corresponding to the $n + 2$ surjective maps from $[n]$ to $[1]$. 
Label them as $\alpha_i, -1 \leq i \leq n$.
So for each $n$, the map $ \gamma: A\times \D[1] \rightarrow B$ is determined by $n+2$ maps $\gamma^n_i: A_n \rightarrow B_n$ each corresponding to $\alpha_i \in \D[1]_n$.
For a temporary measure we call $\gamma$ as the middle map.

The following lemma is evident 

\begin{lemma}\label{homotopy-relation}
	Let $f, f', g, g', h$ be simplicial maps from $A$ to $B$, where $A$ $B$ are simplicial objects in abelian category $\A$. We have
	\begin{enumerate}
		\item $f \simeq f$
		\item If $f \simeq f'$ and $g \simeq g'$, then $f + g \simeq f' + g'$
		\item If $f \simeq f'$, then $(-f) \simeq (-f')$, $f-g \simeq 0$ and $g \simeq f$
		\item If $f \simeq g$ and $g\simeq h$, then $f \simeq h$
	\end{enumerate} 
\end{lemma}

\begin{proof}
	$f \simeq f$, as we can define $\gamma_i = f$ for all applicable $i$ in the commutative diagram \ref{simplicial-homotopy-diagram}.

	If $f\simeq g$ with corresponding $\gamma$ as middle maps and $f' \simeq g'$ with corresponding $\gamma'$ as middle maps, then $f + f' \simeq g + g'$ with corresponding $\gamma + \gamma'$ as the middle map.

	All other parts of the proof are similar.
\end{proof}

Here is an important lemma 

\begin{lemma}\label{homotopy-chain-homotopy1}
	If $f, g: A \rightarrow B$ are simplicial homotopic, then the induced map $f_{*}, g_{*}$ of normalised chain complexes $N(f), N(g): N(A) \rightarrow N(B)$ are chain homotopic.
\end{lemma}

\begin{proof}
	By lemma \ref{homotopy-relation}, $f \simeq g \iff f-g \simeq 0$. 
	So it suffices to show that if $f \simeq 0$, then $f_* = N(f) \simeq 0$ as chain maps.

	For each $n$, define $s_n = \sum_{i=0}^{n} (-1)^i h_i$, where $h_i$ are the maps in definition \ref{simplicial-homotopy} corresponding to the simplicial homotopy from $0$ to $f$.
	Note that $s_n$ is a map from $A_n$ to $B_{n + 1}$. 
	I claim that 
	\begin{equation}\label{chain-homotopy-eq}
		\d_{n+1} s_n - s_{n-1} \d_n = (-1)^n f,
	\end{equation}
	therefore $\{(-1)^n s_n\}$ is a chain homotopy from $0$ to $f_*$.
\begin{equation*}
	\begin{tikzcd}
		\cdots \arrow{r} & 
		N_n(A) \arrow{r}{\d_n} \arrow{d}{f_{*n}} &
		\cdots \arrow{r}{\d_2} &
		N_1(A) \arrow{r}{\d_1} \arrow{d}{f_{*1}} \arrow{dl}{s_1}&
		N_0(A) \arrow{r} \arrow{d}{f_{*0}} \arrow{dl}{s_0}&
		0 \\
		\cdots \arrow{r} &
		N_n(B) \arrow{r}{\d_n} &
		\cdots \arrow{r}{\d_2} &
		N_1(B) \arrow{r}{\d_1} &
		N_0(B) \arrow{r} &
		0
	\end{tikzcd}
\end{equation*}
	Equation \eqref{chain-homotopy-eq} can be proved purely combinatorially.
	For the case $n = 0$, $s_0 = h_0$, and $d_1h_0$ by equation \eqref{homotopy1} is $f$.

	For the case $n = 1$, $s_1 = h_0 - h_1$.
	Therefore
	\begin{dmath}
		\d_{2}s_1 - s_0 \d_1 = \d_2 h_0 - \d_2 h_1 - h_0 \d_1
		= h_0 \d_1 - h_0 \d_1 - \d_2 h_1 \quad \text{by equation \eqref{homotopy2}}
		= -f \quad \text{by equation \eqref{homotopy1}}
	\end{dmath}

	In general, we have 
	$$
	\d_{n+1} s_n = \sum_{i=0}^{n} (-1)^i \d_{n+1} h_i = (-1)^n \d_{n+1} h_n + \sum_{i=0}^{n-1} (-1)^i h_i \d_n
	$$
	And 
	$$
	s_{n-1} \d_n = \sum_{i=0}^{n-1} (-1)^i h_i \d_n
	$$
	Subtracting the two equations we have
	$$\d_{n+1} s_n - s_{n-1} \d_n = (-1)^n \d_{n+1} h_n = (-1)^n f$$
	which is the desired equation.
\end{proof}

There is a converse to lemma \ref{homotopy-chain-homotopy1}. 

\begin{lemma}\label{homotopy-chain-homotopy2}
	For two chain homotopic maps $f, g: C \rightarrow C'$, the corresponding simplicial maps $K(f), K(g): K(C) \rightarrow K(C')$ are simplicially homotopic \cite{weibel}.
\end{lemma}

\begin{proof}
	Assuming we have the chain homotopy $s_n: C_n \rightarrow C'_{n+1}$ from $f$ to $g$. 
	We shall define $h_i: K(C)_n \rightarrow K(C'_{n+1})$ according to the following procedure. 
	\begin{enumerate}
		\item On the unique summand $C_n$ of $K_n(C)$ corresponding to the identity map $\text{id}_{[n]}: [n] \to [n]$, define
		\begin{equation}
			h_i|_{C_n} = \begin{cases}
				\sigma_i f & i < n - 1 \\
				\sigma_{n - 1} f - \sigma_{n}s_{n-1}d & i = n - 1 \\
				\sigma_{n }( f - s_{n-1}d) - s_n & i = n  \\
			\end{cases}
		\end{equation}
	\item On the summand $C_{n-1}[\eta]$ of $K(C)_n$ corresponding to a surjective map $\eta: [n] \to [n - 1]$. 
			Let $j$ be the integer such that $\eta(j) = \eta(j+1)$. 
			We can write $\eta =  \text{id}_{n-1} \circ \eta^j$, where $\eta^j$ is the $j$-th degenerate map in $\D$. 
			Note that $\epsilon^i$ maps $C_{n-1}[\text{id}_{n-1}]$ isomorphically to $C_{n-1}[\eta^i]$.
			This is because we have the following commutative diagram 
\begin{equation*}
	\begin{tikzcd}
		{[n - 1]} \arrow{r}{\epsilon^i} \arrow{d}{\text{id}} & {[n]} \arrow{d}{\eta^i} \\
		{[n - 1]} \arrow{r}{\text{id}} & {[n - 1]}
	\end{tikzcd}
\end{equation*}
We have already defined the maps $h_i$ on $C_{n-1}[\text{id}_{n-1}]$, define $h'_i$ be the restriction of $h_i$ to $C_{n-1}[\text{id}_{n-1}]$. 
We define 
$$
h_i|_{C_{n-1}[\eta]} =
\begin{cases}
	\sigma_j h'_{i-1} & j < i\\
	\sigma_{j+1} h'_{i} & j \geq i
\end{cases}
$$
\item On all other summands $C_p[\eta]$ of $K(C)_n$, with $\eta: [n] \rightarrow [p]$, find the greatest integer $j$ such that $\eta(j) = \eta(j + 1)$.
	We can write $\eta = \eta' \eta_j$,  and proceed similarly as in step 2.
	\end{enumerate}

	It is a lengthy but straightforward verification to check that the maps $h_i$ defined above satisfy equations \eqref{homotopy1} - \eqref{homotopy4} in definition \ref{simplicial-homotopy}.
\end{proof}
