\documentclass[twocolumn]{article}

\input{./preamble.tex}

\begin{document}

\begin{fdefi}{Notation}{}
	\begin{enumerate}
		\item $W, U, V, W_i, U_i, V_i$, $i \in \Z$, denote open set;
		\item $X, Y$ denotes topological space;
		\item At most countable means countable or finite, countable means there is bijection to $\N$
	\end{enumerate}
\end{fdefi}
\hrulefill

\section{Basics}

\begin{defi}[limit point]
	A \emph{limit point} of a set $A$ is the \emph{accumulation point}.
	Let $A'$ denote the set of limit points of $A$.
\end{defi}

\begin{defi}
	\begin{enumerate}
		\item \emph{closure} of set $A$ is 
			$$
				\closure{A} = \bigcap \{ U \mid U \text{ is closed and } A \subseteq U \}
			$$
		\item \emph{interior} of set $A$ is 
			$$
				\interior{A} = \bigcup \{ U \mid U \text{ is open and } U \subseteq A \}
			$$
		\item \emph{boundary} of set $A$ is 
			$$
			\partial A = \closure{A} \smallsetminus \interior{A} 
			$$
		\item A set $A$ in topological space $X$ is dense if $\closure{A} = X$.
	\end{enumerate}
\end{defi}

\begin{thm}[On closure and interior]
	\begin{enumerate}
		\item $\closure{A} = A \cup A'$.
	\end{enumerate}
\end{thm}

\begin{thm}
	Suppose $f : X \rightarrow Y$
	\begin{enumerate}
		\item $f$ is continuous if and only if $f(\closure{A}) \subseteq \closure{f(A)}$  for all $A \subseteq X$
		\item $f$ is closed if and only if $f(\closure{A}) \supseteq  \closure{f(A)}  $ for all $A \subseteq X$
		\item $f$ is continuous if and only if $f^{-1}(\interior{B}) \subseteq \interior{f^{-1}(B)}$ for all $B \subseteq Y$ 
		\item $f$ is open if and only if $f^{-1}(\interior{B}) \supseteq \interior{(f^{-1}(B))}$ for all $B \subseteq Y$
	\end{enumerate}
\end{thm}

\begin{thm}
	A subset of $\R$ is open if and only if it is the at most countable union of disjoint non-empty open interval.
\end{thm}

\begin{remark}
	Any family of non-empty open intervals in $\R$ is at most countable. 
	This is because any non-empty open interval in $\R$ contains at least one rational number.
\end{remark}

\begin{defi}
	A metric space is complete if every Cauchy sequence converges.
\end{defi}

\begin{defi}
	A collection of subset $\B$ of $X$ ($\B \subseteq \P(X)$ ) is a basis for topology on $X$ if 
	\begin{enumerate}
		\item $\cup \B = X$
		\item For any $U, V \in \B$ there exists $W \in \B$ such that $W \subset  U \cap V$
	\end{enumerate}
\end{defi}

\subsection{Countability}

\begin{defi}
	A topological space is \emph{first countable} if there exists a countable neighborhood bases at each point.
	A neighborhood basis at a point $p$ is a collection of set $\B_p$ such that every neighborhood at $p$ is contained in some $U \in \B_p$.
\end{defi}

\begin{thm}
	Every metric space is first countable.
\end{thm}

\begin{thm}
	Suppose $X$ is a first countable space, $A$ is any subset of $X$, and $x$ is any point of $X$.
	\begin{enumerate}
		\item $x \in \closure{A}$ if and only if $x$ is a limit of a sequence of points in $A$.
		\item $x \in \interior{A}$ if and only if every sequence in $X$ converging to $x$ is eventually in $A$. 
		\item $A$ is closed in $X$ if and only if $A$ contains every limit of every convergent sequence of points in $A$.
		\item $A$ is open in $X$ if and only if every sequence in $X$ converging to a point of $A$ is eventually in $A$.
	\end{enumerate}
\end{thm}

\begin{defi}
	A topological space is \emph{second countable} if it has a countable bases.
\end{defi}

\begin{thm}
	Supppose $X$ is a second countable space.
	\begin{enumerate}
		\item $X$ is first countable.
		\item $X$ contains a countable dense set.
		\item Every open cover of $X$ has countable subcover.
	\end{enumerate}
\end{thm}

\section{New Topologies From Old}

\begin{thm}
	If $f$ is a continuous map. 
	Restricting thge domain, codomain, or expanding the ccodomain does not affect the continuity.
\end{thm}

\begin{example}
	Let $M$ be a subspace of $X$ with subspace topology.
	\begin{enumerate}
		\item If $X$ is hausdorff so is $M$.
	\end{enumerate}
\end{example}

\begin{defi}[Weak Topology]
	Assuming $X$ is a set and $X_i, T_i$ are topologies and $f_i: X \rightarrow X_i$. 
	The weak topology of $X$ generated by $f_i$ is the smallest topology on $X$ which make all of the $f_i$ continuous.
\end{defi}

\begin{defi}[Quotient Topology]
	Let $X$ be a topological space, $Y$ any set, and $f: X \rightarrow Y$ a surjective map.
	Define a subset $U \subset Y$ to be open if and only if $f^{-1}(U)$ is open in $X$. 
	This is the quotient topology.
\end{defi}

\begin{defi}[Equivalence relationship]
	An relationship $\sim$ is an equivalence relationship if it is 
	\begin{enumerate}
		\item reflexive: $x \sim x$ for all $x$
		\item symmetric: $x \sim y \implies y \sim x$
		\item transitive: if $x \sim y $ and $y \sim z$, then$ \implies x \sim z$
	\end{enumerate}
\end{defi}

\begin{example}
	Real projective space $\R P^n$ is $\S^n \slash \sim$, where $x \sim y $ if and only if $ x = y$ or $x = -y$.
\end{example}

\section{Compact}

\begin{thm}[Properties of Compact Spaces]
	\begin{enumerate}
		\item Every closed subset of a compact space is compact.
		\item Every compact subset of a Hausdorff space is closed.
		\item Every compact subset of a metric space is bounded.
		\item Every product of compact spaces is compact.
		\item Every quotient of a compact space is compact.
	\end{enumerate}
\end{thm}

\begin{defi}
	A set $X$ is \emph{limit point compact} if every infinite subset of $X$ has a limit point in $X$. 
	A set $X$ is \emph{sequentially compact} if every sequence in $ X $ has convergent subsequence in $X$.
\end{defi}

\begin{thm}
	Compact implies limit point compact.
\end{thm}

\begin{thm}
	For first countable Hausdorff space, limit point compactness implies sequential compactness.
\end{thm}

\begin{thm}
	For metric space and second countable space, sequential compactness implies compactness.
\end{thm}

\begin{thm}[Closed Map Theorem]
	Let $X$ be compact and $Y$ be Hausdorff. $f: X \rightarrow Y$ continuous, then
	\begin{enumerate}
		\item $f$ is a closed map
		\item If $f$ is injective it is a topological embedding
		\item If $f$ is surjective it is a quotient map 
		\item If $f$ is bijective it is a homeomorphism
	\end{enumerate}
\end{thm}

\begin{thm}
	$X \times Y$ is compact if and only if both $X$ and $Y$ are comapct.
\end{thm}

\begin{thm}
	If $X$ is a compact Hausdorff space and $q: X \rightarrow Y$ is a quotient map, then $Y$ is hausdorff if and only if $f$ is a closed map.
\end{thm}

\begin{defi}[One Point Compactification]
	Let $X$ abe a topological space. 
	The one point compacitifaction of $X$ is the topological space $X^* = X \cup \{\infty\}$ such with open sets either 
	\begin{enumerate}
		\item $U \subseteq X$ is open in $X$ or
		\item $U = X^* \smallsetminus K$ where $K$ is compact and closed in $X$.
	\end{enumerate}
\end{defi}

\begin{defi}[Locally compact]
	A topological space is locally compact if and only if for every point $x$ there exists a neighborhood $U$ of $x$ such that $\closure{U}$ is compact, or equivalently, $U$ is contained in a compact set.
\end{defi}

\begin{thm}
	The one point compactification of $X$ is hausdorff if and only if $X$ is hausdorff and locally compact.
\end{thm}

\section{Normal}

\begin{defi}[Normal]
	A topological space $X$ is normal if and only if every two disjoint closed sets can be separated by disjoint open sets.
\end{defi}

\begin{thm}
	$X$ if normal if and only if for all $A \subset B$, where $A$ is closed and $B$ is normal, there exists open set $B'$ and closed set $A'$ such that 
	$$
		A \subset B' \subset A' \subset B
	$$
\end{thm}

\begin{thm}[Urysohn's Lemma]
	Let $X$ be a normal space and $A, B$ be disjoint closed sets in $X$. 
	Then there exists a continuous function $f: X \rightarrow [0, 1]$ such that $f(A) = 0$ and $f(B) = 1$.	
\end{thm}

\begin{thm}[Tietze Extension Theorem]
	Let $X$ be a normal space and $A$ be a closed subset of $X$. 
	Then every continuous function $f: A \rightarrow [0, 1]$ can be extended to a continuous function $F: X \rightarrow [0, 1]$.
\end{thm}

\begin{defi}
	For a compact topological space $X$, we may set an algebra of continuous function $C(X)$, starting from constant function and function given by Tietze extension theorem. 

	We define the norm of $f \in C(X)$ as $\sup |f(x)|$.
\end{defi}

\begin{thm}[Stone-Weierstrass Theorem]
	Let $A$ denote the subalgebra of $C(X)$ consisting of all functions that are constant and functions guaranteed by Tietze theorem. 
	$\closure{A} = C(X)$, that is, for all $g$ and for all $\epsilon$, there exists $f \in A$ such that $\sup |g(x) - f(x)| < \epsilon$.
\end{thm}

\section{Connecteness}

\begin{thm}
	Every product of finitely many \emph{connected} spaces is connected. 
	Every quotient of connected space is connected.

	Every product of finitely many \emph{path-connected} spaces is connected. 
	Every quotient of path-connected space is connected.
\end{thm}

\begin{thm}[Connected Components]
	Each connected component of a topological space is closed.

	Each component is a disjoint union of path components.
\end{thm}

\begin{defi}[Locally connected]
	$X$ is locally (path-)connected if every point $x$ is contained in a (path-)connected neighborhood.
\end{defi}

\begin{thm}
	A topological space can be connected but not locally connected. It can be locally connected but not connected.
\end{thm}

\begin{thm}
	If $X$ is locally connected, every connected component of $X$ is open.
\end{thm}

\begin{thm}
	If $X$ is locally path-connected, it is connected if and only if it is path-connected.
\end{thm}

\end{document}

